HTW

### 2024-02-16 Manuscript/manuscript.qmd
try rendering manuscript itself

All data processing and statistical analyses were performed in R version 4.31 @rcoreteamLanguageEnvironmentStatistical2020. To assess differences between groups, we used Bayesian Mixed Effects Regression. Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019a. Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level. Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as circumventing convergence issues common to the frequentist analogues of our mixed models. For each model, we report the median values of the posterior distribution, and 95% credible intervals.

@@

```{r}
#| label: fig-e1-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
#| layout-ncol: 2
#| include: true

@@

```{r}
#| label: fig-e1-bmm-bx2
#| fig-cap: Slope distributions between condition
#| fig-subcap: ["Slope estimates by participant - ordered from lowest to highest within each condition. ", "Destiny of slope coefficients by training group"]
#| layout-ncol: 2
#| fig-height: 9
#| fig-width: 10
#| include: true

@@

```{r}
#| label: tbl-e2-test-nf-vx
#| tbl-cap: "Testing vx - Empirical Summary"
#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
#| layout-ncol: 2

@@

```{r setup3b, include=FALSE}
testE3 <- readRDS(here("data/e3_08-04-23.rds")) |> filter(expMode2 == "Test") 
e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

@@

```{r}
#| label: fig-e3-test-dev
#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder)
```

```{r}
#| label: tbl-e3-bmm-dist
#| tbl-cap: "Experiment 3. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
#| eval: true

@@

```{r}
#| label: fig-e3-test-vx
#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 12
#| fig-height: 13

# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")

@@

# column: screen-inset-right

@@

```{r}
#| label: tbl-e3-bmm-vx
#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
#| eval: true
e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
mt4 <-GetModelStats(e3_vxBMM ) |> kable(booktabs=T)
mt4

@@

{{< include ../Simulations/htw_exam.qmd >}}

>>>>

All data processing and statistical analyses were performed in R version 4.31 @rcoreteamLanguageEnvironmentStatistical2020. To assess differences between groups, we used Bayesian Mixed Effects Regression. Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019. Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level. Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as circumventing convergence issues common to the frequentist analogues of our mixed models. For each model, we report the median values of the posterior distribution, and 95% credible intervals.

@@

```{r}
#| label: fig-e1-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
#| layout-ncol: 1
#| include: true

@@

```{r}
#| label: fig-e1-bmm-bx2
#| fig-cap: Slope distributions between condition
#| fig-subcap: ["Slope estimates by participant - ordered from lowest to highest within each condition. ", "Destiny of slope coefficients by training group"]
#| layout-ncol: 1
#| fig-height: 9
#| fig-width: 10
#| include: true

@@

```{r}
#| label: tbl-e2-test-nf-vx
#| tbl-cap: "Testing vx - Empirical Summary"
#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
#| layout-ncol: 1

@@

```{r setup3b}
testE3 <- readRDS(here::here("data/e3_08-21-23.rds")) |> filter(expMode2 == "Test") 
e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

@@

```{r}
#| label: fig-e3-test-dev
#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
```

```{r}
#| label: tbl-e3-bmm-dist
#| tbl-cap: "Experiment 3. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"

@@

```{r}
#| label: fig-e3-test-vx
#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 12
#| fig-height: 13
# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")

@@

@@

```{r}
#| label: tbl-e3-bmm-vx
#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"

e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
mt4 <-GetModelStats(e3_vxBMM ) |> kable(booktabs=T)
mt4

@@

### Computational Modelling

{{< include ../Model/htw_model.qmd >}}
